Interactively Visualizing Multivariate Market Segmentation Using the R Package Lionfish

### 2024-10-02 manuscript.tex
changed capitalization of references

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Matthias Medl, Dianne Cook, Ursula Laa} %% comma-separated
\Plaintitle{lionfish} %% without formatting
\Shorttitle{lionfish} %% a short title (if necessary)

@@

The majority of \texttt{lionfish} was written in Python, while the R side of the package handles setting up the Python environment within the interactive interface is being run, launching the interactive tour, and generating new tours when initiated through the interface. To incorporate the functionality of the \texttt{tourr} package without translating large portions of its code from R to Python, the \texttt{reticulate} package was used. This approach allows \texttt{lionfish} to automatically benefit from updates to \texttt{tourr}.

>>>>

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Matthias Medl, Dianne Cook, Ursula Laa} %% comma-separated
\Plaintitle{Interactively Visualizing Multivariate Market Segmentation Using the R Package Lionfish} %% without formatting
\Shorttitle{Market Segmentation using Lionfish} %% a short title (if necessary)

@@

The majority of \texttt{lionfish} was written in Python \citep{python}, while the R \citep{R} side of the package handles setting up the Python environment within the interactive interface is being run, launching the interactive tour, and generating new tours when initiated through the interface. To incorporate the functionality of the \texttt{tourr} package without translating large portions of its code from R to Python, the \texttt{reticulate} package was used. This approach allows \texttt{lionfish} to automatically benefit from updates to \texttt{tourr}.
